---
title: "A title for the analysis"
output: 
  html_document:
    theme: lumen
    toc: true
    toc_float:
      collapsed: false
    code_folding: show
---

```{r include=FALSE}
knitr::opts_chunk$set(echo=TRUE, message=FALSE, warning=FALSE, fig.width=8, tidy=TRUE)
```


I find this type of document perfect for tutorials. 
I used it to show the commands and output for a [R workshop](https://github.com/jmonlong/HGSS_Rworkshops/blob/master/Advanced-Tidyverse-Bioconductor-2018/HGSS-Rworkshop2018-advanced-liveScript.md).

It's also good to link code to a publication. 
For example, we created a GitHub repository with the code and outputs of our recent paper (see [epipopsv repo](https://github.com/jmonlong/epipopsv) and the `reports` folder).
It shows how each figure/table was produced using R Markdown.

```{r libs}
library(dplyr)
library(knitr)
library(broom)
library(ggplot2)
```


## First part

You can write a short description about what this part is about, what you want to achieve, etc.
Potentially explain how you got the input data and what it is.

For example, let's say I want to create some fake normal data to later test differences between two groups.

```{r sim}
N = 40
df = tibble(group=rep(1:2,N), var=rnorm(2*N,0,10)) %>% mutate(data=rnorm(n(), group)+var)
df %>% head %>% kable
```

## Second part

Now we want to test differences between the two groups.

### t-test

```{r ttest}
tt.o = t.test(subset(df, group==1)$data, subset(df, group==2)$data)
tt.o
```

Not significant, the p-value is `r tt.o$p.value`.


### Controlling for something

A linear model that controls for the `var` column.

```{r lm}
library(broom)
lm(group ~ data + var, data=df) %>% tidy %>% kable
```

Now it's significant, yeay !

## Third part

Maybe it's time for a graph.

```{r graph}
library(ggplot2)
ggplot(df, aes(x=data, y=var, colour=factor(group))) + geom_point()
```
