---
title: "A title for the analysis"
# author metadata, esp. used for scientific articles
author:
  - name: Jeremy Leipzig
    footnote: Corresponding author
    affiliation: "Metadata Research Center, Drexel University, College of Computing and Informatics, Philadelphia PA, USA"
    orcid: "0000-0001-7224-9620"
  - name: Daniel Nüst
    affiliation: "Institute for Geoinformatics, University of Münster, Germany"
    orcid: "0000-0002-0024-5046"
    email: daniel.nuest@uni-muenster.de

# parameters to manipulate workflow; defaults can be changed when compiling the document
params:
  year: 2020
  region: "Europe"
  printcode: TRUE
  data: file.csv
  max_n: 42

# configuration and styling of different output document formats
output: 
  html_document:
    theme: lumen
    toc: true
    toc_float:
      collapsed: false
    code_folding: show
    self_contained: true
  pdf_document:
    toc: yes
    fig_caption: yes
    df_print: kable
linkcolor: blue

# field values can be generated from code
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

<!-- inspiration/sources for fake front matter: https://bookdown.org/yihui/rmarkdown/params-declare.html, https://github.com/nuest/reproducible-research-at-giscience/blob/master/paper/reproducible-research-at-giscience.Rmd -->

```{r include=FALSE}
knitr::opts_chunk$set(echo=TRUE, message=FALSE, warning=FALSE, fig.width=8, tidy=TRUE)
```


I find this type of document perfect for tutorials. 
I used it to show the commands and output for a [R workshop](https://github.com/jmonlong/HGSS_Rworkshops/blob/master/Advanced-Tidyverse-Bioconductor-2018/HGSS-Rworkshop2018-advanced-liveScript.md).

It's also good to link code to a publication. 
For example, we created a GitHub repository with the code and outputs of our recent paper (see [epipopsv repo](https://github.com/jmonlong/epipopsv) and the `reports` folder).
It shows how each figure/table was produced using R Markdown.

```{r libs}
library(dplyr)
library(knitr)
library(broom)
library(ggplot2)
```


## First part

You can write a short description about what this part is about, what you want to achieve, etc.
Potentially explain how you got the input data and what it is.

For example, let's say I want to create some fake normal data to later test differences between two groups.

```{r sim}
N = 40
df = tibble(group=rep(1:2,N), var=rnorm(2*N,0,10)) %>% mutate(data=rnorm(n(), group)+var)
df %>% head %>% kable
```

## Second part

Now we want to test differences between the two groups.

### t-test

```{r ttest}
tt.o = t.test(subset(df, group==1)$data, subset(df, group==2)$data)
tt.o
```

Not significant, the p-value is `r tt.o$p.value`.


### Controlling for something

A linear model that controls for the `var` column.

```{r lm}
library(broom)
lm(group ~ data + var, data=df) %>% tidy %>% kable
```

Now it's significant, yeay !

## Third part

Maybe it's time for a graph.

```{r graph}
library(ggplot2)
ggplot(df, aes(x=data, y=var, colour=factor(group))) + geom_point()
```
